### 2016-02-02 Projects/DelCo_2012/Report/DelCo_2012.tex
edits to CAF report

>>>>

Demonstration of Biodegradable, Environmentally Safe, Non-toxic Fire Suppression Liquids NISTIR 6191 was published in 1998~\cite{Madrzykowski:4}. That study examined a broad range of tests in order to determine those parameters that most critically effect fire-fighting performance.  The types of experiments conducted and the impact of additives relative to water are included in Table~\ref{tab:agent_tests}:

\begin{table}[!ht]
\centering
\captionof{table}{Tests to Assess Fire Fighting Agents Compared to Water}\label{tab:agent_tests}
\begin{tabular}{lcc}
\toprule[1.5pt]
Test                                    & Similar Performance & Enhanced Performance \\
\midrule
Specific Heat                           &  \checkmark         &                      \\
Fuel Cooling and Penetration            &                     &  \checkmark          \\
Mass Retention                          &                     &  \checkmark          \\
Ignition Inhibition                     &                     &  \checkmark          \\
Drop Size                               &  \checkmark         &                      \\
Contact Angle                           &  \checkmark         &                      \\
Tire Fire Suppression                   &  \checkmark         &                      \\
Wood Crib Suppression                   &  \checkmark         &                      \\
Heptane Fire Suppression                &  \checkmark         &                      \\
Magnesium \& Titanium Fire Suppression  &  \checkmark         &                      \\
Smoke Generation                        &  \checkmark         &                      \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

Based on the results of the study, the fire fighting agents, commonly referred to as Class A foams, were superior to water in cooling and penetrating the fuels, mass retention and ignition inhibition.  All of these features enable the agents, when applied in the form of foam, to provide enhanced radiation exposure protection to a structure relative to plain water.  The foams enhance the water by keeping the water in place on vertical surfaces such as walls and the reduced interfacial surface tension allows the water to penetrate absorbent fuels.  These enhancements also make the agents valuable tools for mop-up. Many of the experiments conducted during this study: specific heat, drop size, contact angle, wood crib suppression, smoke generation and Class D fire suppression yielded similar results for both Class A foams and plain water.
